The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-08 full_paper_draft.Rmd
made line graphs for variation

```
The drought data also spans the years 2005-2012 and shows the frequency of droughts in each municipality by year.

@@

@@

@@

probitMod_register <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_r <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_u <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

@@

probitMod_register_lt <- glm(register ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_lr <- glm(register ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_lu <- glm(register ~ lag_floods + lag_f_secondary + lag_flood_lny + lag_droughts + lag_d_secondary + lag_drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

@@

probitMod_registerx <- glm(register ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_rx <- glm(register ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_ux <- glm(register ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

@@

probitMod_register_g <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + mountains + plains + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_rg <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + mountains + plains + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_ug <- glm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + mountains + plains + year_factor, data = urban, family=binomial(link="probit"))

@@

model_register_t <- lm(register ~ floods + flood_secondary + flood_lny + droughts + drought_secondary + drought_lny + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data)

@@

model_register_r <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural)

@@

model_register_u <- lm(register ~ floods + flood_secondary + droughts + drought_secondary + age + female + lny + child + grandchild + num_children + secondary + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban)

>>>>

The drought data also spans the years 2005-2012 and shows the frequency of droughts in each municipality by year.

@@

reg_data %>%
   group_by(attend, register) %>%
   summarise(n = n())

@@

```{r creating line graphs for variation within variables, echo = F, message = F}

Beni <- subset(flood_summary, dept == "Beni" & year > 2003, select = c("year", "floods")) 
Chuq <- subset(flood_summary, dept == "Chuquisaca" & year > 2003, select = c("year", "floods"))
Pando <- subset(flood_summary, dept == "Pando" & year > 2003, select = c("year", "floods"))
SantaCruz <- subset(flood_summary, dept == "Santa Cruz" & year > 2003, select = c("year", "floods"))
Oruro <- subset(flood_summary, dept == "Oruro" & year > 2003, select = c("year", "floods"))
Potosi <- subset(flood_summary, dept == "Potosi" & year > 2003, select = c("year", "floods"))
LaPaz <- subset(flood_summary, dept == "La Paz" & year > 2003, select = c("year", "floods"))
Tarija <- subset(flood_summary, dept == "Tarija" & year > 2003, select = c("year", "floods"))
Cocha <- subset(flood_summary, dept == "Cochabamba" & year > 2003, select = c("year", "floods"))
# Create a first line
plot(LaPaz, type = "b", frame = FALSE, pch = 19, 
     col = "red", xlab = "year", ylab = "flood counts")
# Add lines
lines(Potosi, pch = 18, col = "orange", type = "b", lty = 1)
lines(Oruro, pch = 18, col = "orangered4", type = "b", lty = 1)
lines(Beni, pch = 18, col = "green", type = "b", lty = 1)
lines(Pando, pch = 18, col = "yellow", type = "b", lty = 1)
lines(SantaCruz, pch = 18, col = "green4", type = "b", lty = 1)
lines(Cocha, pch = 18, col = "midnightblue", type = "b", lty = 1)
lines(Tarija, pch = 18, col = "mediumorchid1", type = "b", lty = 1)
lines(Chuq, pch = 18, col = "blue", type = "b", lty = 1)
# Add a legend to the plot
legend("topleft", legend=c("LaPaz", "Potosi", "Oruro", "Beni", "Pando", "SantaCruz", "Cochabamba", "Tarija", "Chuquisaca"), col=c("red", "orange", "orangered4", "green", "yellow", "green4", "midnightblue", "mediumorchid1", "blue"), lty = 1:2, cex=0.8)

@@

probitMod_register <- glm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_r <- glm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_u <- glm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

@@

probitMod_register_lt <- glm(register ~ lag_floods + lag_flood_lny + lag_droughts + lag_drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_lr <- glm(register ~ lag_floods + lag_flood_lny + lag_droughts + lag_drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_lu <- glm(register ~ lag_floods + lag_flood_lny + lag_droughts + lag_drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

@@

probitMod_registerx <- glm(register ~ floods + flood_pov + droughts + drought_pov + age + female + extr + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_rx <- glm(register ~ floods + flood_pov + droughts + drought_pov + age + female + extr + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_ux <- glm(register ~ floods + flood_pov + droughts + drought_pov + age + female + extr + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

@@

probitMod_register_g <- glm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + mountains + plains + year_factor, data = reg_data, family=binomial(link="probit"))

@@

probitMod_register_rg <- glm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + mountains + plains + year_factor, data = rural, family=binomial(link="probit"))

@@

probitMod_register_ug <- glm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + mountains + plains + year_factor, data = urban, family=binomial(link="probit"))

@@

model_register_t <- lm(register ~ floods + flood_lny + droughts + drought_lny + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = reg_data)

@@

model_register_r <- lm(register ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural)

@@

model_register_u <- lm(register ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban)
